Sweat electrolytes and CFTR activity in the era of CFTR modulators

### 2022-03-01 Edith Zemanick/Sweat Test/sweat_test_analysis.Rmd
Update sweat_test_analysis.Rmd

```{r setup, include=FALSE}
library(arsenal)
library(tidyverse)
library(performance)
library(knitr)
knitr::opts_chunk$set(echo = FALSE)
if(Sys.info()["sysname"] == "Windows"){
  home_dir = "S:/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Edith Zemanick/Sweat Test"
} else if (Sys.info()["sysname"] == "Linux"){
  home_dir = "~/UCD/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Edith Zemanick/Sweat Test"
} else if (Sys.info()["sysname"] == "Darwin"){
  home_dir = "/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Edith Zemanick/Sweat Test"
}
knitr::opts_knit$set(root.dir = home_dir)
rm(home_dir)
```

```{r}
# Import data
df = read.csv("./Data_Raw/Copy of Sweat Tests_AllFor202558_revised01Feb2021.csv",na.strings = "")
# Filter per Maxie's code
df = df %>% 
  filter(Age.at.Test.in.Years < 50,
         !(Diagnosis == "Non-CF" & PatientID %in% 
             c(22,23,24,29,31,474,483,484,485,505,510,785,791,792,793))) %>% 
  distinct(.) %>% filter(Sex != "",Demographics.Available == "TRUE") %>%
  mutate(Age.at.Test.in.Days = Age.at.Test.in.Weeks*7)
# Add modulator info

```

@@

```{r results='asis'}
t1_df = df %>% filter(Age.at.Test.in.Days >= 2) %>%
  group_by(PatientID) %>% arrange(Age.at.Test.in.Weeks) %>%  filter(row_number()==1)
t1 = tableby(Method ~ Sex,data = t1_df)
summary(t1)
```

>>>>

```{r setup, include=FALSE}
library(arsenal)
library(tidyverse)
library(performance)
library(knitr)
knitr::opts_chunk$set(echo = FALSE)
if(Sys.info()["sysname"] == "Windows"){
  home_dir = "S:/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Edith Zemanick/Sweat Test"
} else if (Sys.info()["sysname"] == "Linux"){
  home_dir = "~/UCD/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Edith Zemanick/Sweat Test"
} else if (Sys.info()["sysname"] == "Darwin"){
  home_dir = "/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Edith Zemanick/Sweat Test"
}
knitr::opts_knit$set(root.dir = home_dir)
rm(home_dir)
source("~/GitHub/CF/get_genotype_class_severity.R")
```

```{r}
# Import data
df = read.csv("./Data_Raw/Copy of Sweat Tests_AllFor202558_revised01Feb2021.csv",na.strings = "")
df$Diagnosis = factor(df$Diagnosis,
                      levels = c("CFTR-related disorder","CRMS","Cystic Fibrosis","Non-CF","Normal"),
                      labels = c("CFTR-related disorder","CRMS","Cystic Fibrosis","Non-CF","Non-CF"))
# Filter per Maxie's code
df = df %>% 
  filter(Age.at.Test.in.Years < 50,
         !(Diagnosis == "Non-CF" & PatientID %in% 
             c(22,23,24,29,31,474,483,484,485,505,510,785,791,792,793))) %>% 
  distinct(.) %>% filter(Sex != "",Demographics.Available == "TRUE") %>%
  mutate(Age.at.Test.in.Days = Age.at.Test.in.Weeks*7)
# Add modulator info
cftr = read.csv("./Data_Raw/Copy of Report CFTR Modulators.csv")
df$Modulator = apply(df,1,function(r){
  mod = cftr[cftr$Patient.ID == as.numeric(r["PatientID"]),]
  if (any(duplicated(mod$Age.at.Start..years.))){
    mod = mod[-which(duplicated(mod$Age.at.Start..years.)),]
  }
  mod = mod[order(mod$Age.at.Start..years.),]
  age = as.numeric(r["Age.at.Test.in.Years"])
  as.character(cut(age,c(-Inf,mod$Age.at.Start..years.,Inf),
                   labels = c("None",mod$Modulator),right = F))
})
df = left_join(df,cftr,by = c("PatientID" = "Patient.ID"))
# Genotype info
df$geno1 = get_cf_genotype_class_severity(df$Genotypes1)
df$geno2 = get_cf_genotype_class_severity(df$Genotypes2)
df$geno1[df$Diagnosis == "Non-CF"] = "Not CF"
df$geno2[df$Diagnosis == "Non-CF"] = "Not CF"
df$geno_risk = paste(df$geno1,df$geno2,sep = "_")
df$geno_risk = factor(df$geno_risk,
                      levels = c("Mild_Severe","Mild_Unknown","Not CF_Not CF","Severe_Mild","Mild_Mild",
                                 "Severe_Severe","Severe_Unknown","Unknown_Severe","Unknown_Unknown"),
                      labels = c("Low","Low","Not CF","Low","Low","High","Unknown","Unknown","Unknown"))
```

@@

```{r results='asis'}
t1_df = df %>% filter(Age.at.Test.in.Days >= 2) %>%
  group_by(PatientID) %>% arrange(Age.at.Test.in.Weeks) %>%  filter(row_number()==1)
t1 = tableby(Method ~ Sex+Age.at.Test.in.Years+geno_risk,data = t1_df)
summary(t1)
```
